---
title: "MOBY: 1. Data prep"
editor_options: 
  markdown: 
    wrap: 72
---

###Preparations

Libraries \ read in libraries

```{r, results='hide'}
util_libraries <- c("foreign", "reshape2", "stargazer", "arm", "plyr", "tidyverse", "stringr", "qdapRegex", "GGally", "progress", "pracma", "lubridate", "DescTools", "Matrix.utils", "irr", "psych", 'gtools', "Hmisc", "colorspace")
vis_libraries  <- c("ggplot2", "ggrepel", "grid", "gridExtra", "RColorBrewer", "scales", "corrplot", "ggeffects", "cowplot", "plot.matrix", "corrgram", "ggnetwork", "vioplot", "dotwhisker", "sjPlot", "sjlabelled", "sjmisc", "plot3D", "ggpubr", "ggExtra", "ggraph")
stat_libraries <- c("network", "sna", "igraph", "moments", "nortest", "MASS", "randomForest", "sandwich", "lmtest", "gmodels", "margins", "sampleSelection", "pROC", "pscl",  "pwr", "relaimpo", "lme4", "plm", "caret", "ResourceSelection", "rvest", "cluster", "factoextra", "outliers", "acss", 'asbio','akima', 'plotly', 'factoextra', 'interactions', 'robustbase', "sandwich", "modelr", "broom", "mgcv", "stringdist", "sem", "lavaan", "corrr", "misty")

#install.packages(util_libraries)
#install.packages(vis_libraries)
#install.packages(stat_libraries)

for (l in 1:length(util_libraries)){ library(util_libraries[l], character.only = TRUE)}
for (l in 1:length(vis_libraries)){ library(vis_libraries[l], character.only = TRUE)}
for (l in 1:length(stat_libraries)){ library(stat_libraries[l], character.only = TRUE)}
```

Graph theme set

```{r}
theme_set(theme_bw())

dropLeadingZero <- function(l){
  str_replace(l, '0(?=.)', '')
}
```

Clear the workspace

```{r}
rm(list=ls())
```

###Read data

Read files

```{r}
#Main data file, filtered
moby<-read.csv("moby_data1_17_01_2022.csv")

#Main data file, unfiltered
full<-read.csv("old_moby_data.csv")

#Sales data files from various sources
sales1<-read.csv("Video_Games_Sales_as_at_22_Dec_2016.csv") # source: https://github.com/kumartej/DataMining
sales2<-read.csv("vgsales-12-4-2019-short.csv") #source: https://www.kaggle.com/datasets/ashaheedq/video-games-sales-2019
sales3<-read.csv("vgsales.csv") #source: https://www.kaggle.com/datasets/gregorut/videogamesales?select=vgsales.csv

#Sales data 2 variable name to match the other two files
sales2$combined_sales <- sales2$Total_Shipped
sales2$combined_sales[is.na(sales2$Total_Shipped)]<- sales2$Global_Sales[is.na(sales2$Total_Shipped)]

#Later data collection to 2019 (to extract user scores)
big_moby <- read.csv("game_data_0805_2019.csv")
```



Match games with sales data by game name (exact match)
Sales 1
```{r}
n_games <- dim(moby)[1]
match_loc<-matrix(nrow=n_games, ncol=1)

#match game titles from main data and sales data 1
for (i in 1:n_games) {
  #if(i/100==trunc(i/100)){print(i)}
  name <- moby$name[i]
  match_loc[i] <- match(name, sales1$Name)
}

#add sales data at the matched observation
name_compare <- cbind(moby$name, sales1$Name[match_loc])
moby$global_sales1 <- sales1$Global_Sales[match_loc]

#Min sales value - replace zero values with half the min nonzero value
paste("sales1, min sales value = ", min(moby$global_sales1, na.rm=T))
paste("sales1, min nonzero sales value = ", min(moby$global_sales1[moby$global_sales1>0], na.rm=T))
if(min(moby$global_sales1, na.rm=T)==0){
  moby$global_sales1[moby$global_sales2==0] <- min(moby$global_sales1[moby$global_sales1>0], na.rm=T)/2
}

#calculate annual sales
moby$global_sales1_annual <- moby$global_sales1/(2016-moby$year)

#log annual sales
moby$log_global_sales1_annual <- log10(moby$global_sales1_annual)+6

#N of observations with valid sales data
paste("sales1, proportion with sales data = ", round(sum(!is.na(name_compare[,2]))/n_games, digits = 2))
```

Sales 2
```{r}
#It seems that "Total Shipped" and "Global Sales" is the same, and it is in units sold, in millions. Not data about sales in dollars. (Checked with Grand Theft Auto V).
#Missing data of "Total Shipped" is actually "Global Sales".

sales2$new_total_shipped <- sales2$Total_Shipped
sales2$new_total_shipped[is.na(sales2$new_total_shipped)] <- sales2$Global_Sales[is.na(sales2$new_total_shipped)]

n_games <- dim(moby)[1]
match_loc<-matrix(nrow=n_games, ncol=1)

#match game titles from main data and sales data 1
for (i in 1:n_games) {
  #if(i/100==trunc(i/100)){print(i)}
  name <- moby$name[i]
  match_loc[i] <- match(name, sales2$Name)
}

#add sales data at the matched observation
name_compare <- cbind(moby$name, sales2$Name[match_loc])
moby$global_sales2 <- sales2$new_total_shipped[match_loc]

#Min sales value - replace zero values with half the min nonzero value
paste("sales2, min sales value = ", min(moby$global_sales2, na.rm=T))
paste("sales2, min nonzero sales value = ", min(moby$global_sales2[moby$global_sales2>0], na.rm=T))
if(min(moby$global_sales2, na.rm=T)==0){
  moby$global_sales2[moby$global_sales2==0] <- min(moby$global_sales2[moby$global_sales2>0], na.rm=T)/2
}


#calculate annual sales, in millions of units
moby$global_sales2_annual <- moby$global_sales2/(2016-moby$year)

#log annual sales, in units
moby$log_global_sales2_annual <- log10(moby$global_sales2_annual)+6

#N of observations with valid sales data
paste("sales2, proportion with sales data = ", round(sum(!is.na(name_compare[,2]))/n_games, digits = 2))
```

Sales 2 for full data
```{r}
#It seems that "Total Shipped" and "Global Sales" is the same, and it is in units sold, in millions. Not data about sales in dollars. (Checked with Grand Theft Auto V).
#Missing data of "Total Shipped" is actually "Global Sales".

sales2$new_total_shipped <- sales2$Total_Shipped
sales2$new_total_shipped[is.na(sales2$new_total_shipped)] <- sales2$Global_Sales[is.na(sales2$new_total_shipped)]

n_games <- dim(full)[1]
match_loc<-matrix(nrow=n_games, ncol=1)

#match game titles from main data and sales data 1
for (i in 1:n_games) {
  #if(i/100==trunc(i/100)){print(i)}
  name <- full$name[i]
  match_loc[i] <- match(name, sales2$Name)
}

#add sales data at the matched observation
name_compare <- cbind(full$name, sales2$Name[match_loc])
full$global_sales2 <- sales2$new_total_shipped[match_loc]

#Min sales value - replace zero values with half the min nonzero value
paste("sales2, min sales value = ", min(full$global_sales2, na.rm=T))
paste("sales2, min nonzero sales value = ", min(full$global_sales2[full$global_sales2>0], na.rm=T))
if(min(full$global_sales2, na.rm=T)==0){
  full$global_sales2[full$global_sales2==0] <- min(full$global_sales2[full$global_sales2>0], na.rm=T)/2
}


#calculate annual sales, in millions of units
full$global_sales2_annual <- full$global_sales2/(2016-full$year)

#log annual sales, in units
full$log_global_sales2_annual <- log10(full$global_sales2_annual)+6

#N of observations with valid sales data
paste("sales2, proportion with sales data = ", round(sum(!is.na(name_compare[,2]))/n_games, digits = 2))
```


Sales 3
```{r}
n_games <- dim(moby)[1]
match_loc<-matrix(nrow=n_games, ncol=1)

#match game titles from main data and sales data 1
for (i in 1:n_games) {
  #if(i/100==trunc(i/100)){print(i)}
  name <- moby$name[i]
  match_loc[i] <- match(name, sales3$Name)
}

#add sales data at the matched observation
name_compare <- cbind(moby$name, sales3$Name[match_loc])
moby$global_sales3 <- sales3$Global_Sales[match_loc]

#Min sales value - replace zero values with half the min nonzero value
paste("sales3, min sales value = ", min(moby$global_sales3, na.rm=T))
paste("sales3, min nonzero sales value = ", min(moby$global_sales3[moby$global_sales3>0], na.rm=T))
if(min(moby$global_sales3, na.rm=T)==0){
  moby$global_sales3[moby$global_sales3==0] <- min(moby$global_sales3[moby$global_sales3>0], na.rm=T)/2
}

#calculate annual sales
moby$global_sales3_annual <- moby$global_sales3/(2016-moby$year)

#log annual sales
moby$log_global_sales3_annual <- log10(moby$global_sales3_annual)+6

#N of observations with valid sales data
paste("sales3, proportion with sales data = ", round(sum(!is.na(name_compare[,2]))/n_games, digits = 2))
```


Sales data from source 1 and source 3 are identical. Sales 2 has the largest coverage
```{r, fig.width = 4, fig.height = 4}
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...) {
    usr <- par("usr")
    on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    Cor <- abs(cor(x, y, use="complete.obs")) # Remove abs function if desired
    txt <- paste0(prefix, format(c(Cor, 0.123456789), digits = digits)[1])
    if(missing(cex.cor)) {
        cex.cor <- 0.4 / strwidth(txt)
    }
    text(0.5, 0.5, txt,
         cex = 1 + cex.cor * Cor) # Resize the text by level of correlation
}


df <- data.frame(moby$global_sales1,moby$global_sales2,moby$global_sales3)
colnames(df) <- c("sales 1", "sales 2", "sales 3")
#pairs(df)
suppressWarnings({
pairs(df,
      upper.panel = panel.cor,    # Correlation panel
      lower.panel = panel.smooth)
})
```


Big moby user score match
```{r}
n_games <- dim(moby)[1]

match_loc<-matrix(nrow=n_games, ncol=1)

#match game titles from main data and big moby dataset
for (i in 1:n_games) {
  #if(i/100==trunc(i/100)){print(i)}
  name <- moby$name[i]
  match_loc[i] <- match(name, big_moby$game_name)
}

#add user score data at the matched observation
name_compare <- cbind(moby$name, big_moby$game_name[match_loc])
paste("from big moby, proportion mathed = ", round(sum(!is.na(name_compare[,2]))/n_games, digits = 2))

#add user score to those matched
moby$user_score <- big_moby$user_score_mean[match_loc]
paste("from big moby, proportion with user score = ", round(sum(table(moby$user_score))/n_games, digits = 2))
```

Generate a variables list
```{r}
var_list <- cbind(colnames(moby))
```


Creating inclusion variables with user-friendly names
```{r}
moby$mixing <- moby$assortativity_rev_z
moby$bonding <- moby$weighted_cross_edges_ratio_z
moby$incorporating <- moby$female_coreness_log_z
moby$mixing_z <- (moby$mixing-min(moby$mixing, na.rm=T))/sd(moby$mixing)
moby$bonding_z <- (moby$bonding-min(moby$bonding, na.rm=T))/sd(moby$bonding)
moby$incorporating_z <- (moby$incorporating-min(moby$incorporating, na.rm=T))/sd(moby$incorporating)
moby$combined <- moby$mixing*moby$bonding*moby$incorporating
```

Firm-level dataset from means of game level values
```{r, message=FALSE, warning = FALSE}
#developer firm level aggregation
moby_dev_firm_level <- aggregate(moby, list(dev_firm = moby$org_dev), mean)
```


Merge inclusion into 'full' dataset
```{r}
inc_data <- moby[,c("game_id", "blau2", "ratio_core", "num_countries", "mixing", "bonding", "incorporating", "combined")]

full <- left_join(full, inc_data, by='game_id')

full$selection <- 0
full$selection[!is.na(full$num_countries)] <- 1

full$num_countries <- rowSums(full[,129:191])
full$ratio_core[is.na(full$ratio_core)] <- 0
full$blau2[is.na(full$blau2)] <- 0
full$mixing[is.na(full$mixing)] <- 0
full$bonding[is.na(full$bonding)] <- 0
full$incorporating[is.na(full$incorporating)] <- 0
full$combined[is.na(full$combined)] <- 0
```

Save environment
```{r}
save.image(file='Data_prep.RData')
```



